Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-23 introduction.tex
Reworded a paragraph in section 1.2
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1150 ccdd05d5-56c1-461a-bf98-85f6876523b4

\EM{} followup requires estimating the location of the \GW{} source. The
localization uncertainty is dominated by uncertainty in the time of arrival of
the \GW{}s, which is determined by the signal's effective bandwidth and \SNR{}
\citep{Fairhurst2009}. Table~\ref{fig:earlywarning} and Fig.~\ref{fig:sky-localization-accuracy} estimate the
minimum 90\% confidence area versus time for a few rare, loud
coalescence events detectable by Advanced \LIGO{} and Advanced Virgo. A
once-per-year event would have minimum 90\% confidence areas of $1300$~deg$^2$
($3.1$\% of the sky) and $260$~deg$^2$ ($0.63$\% of the sky) at times 25~s and
10~s before coalescence, respectively. The confidence region shrinks
quadratically in area as the overall amplitude of the signal increases. By the
time of merger, the minimum 90\% confidence area shrinks to $0.82$~deg$^2$.

>>>>

\EM{} followup requires estimating the location of the \GW{} source. The
localization uncertainty is dominated by uncertainty in the time of arrival of
the \GW{}s, which is determined by the signal's effective bandwidth and \SNR{}
\citep{Fairhurst2009}. Table~\ref{fig:earlywarning} and figure~\ref{fig:sky-localization-accuracy} show the estimated
minimum 90\% confidence area versus time of the loudest
coalescence events detectable by Advanced \LIGO{} and Advanced Virgo.  Once per year,
we expect to observe an event with a final \SNR\ of 27.4 whose location can be
constrained to about 1300~deg$^2$ (3.1\% of the sky) 25~s before merger, 260~deg$^2$
(0.63\% of the sky) 10~s before merger, and 0.82~deg$^2$ (0.0020\% of the sky) at merger.
